Intensity Modulated Radiation Therapy using Tomotherapy

### 2014-12-02 BME 560/Paper.tex
Updates

\documentclass[10pt,journal,compsoc]{IEEEtran} %draftclsnofoot, 
\usepackage{graphicx}
\graphicspath{ {./_figures/} }
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\usepackage{bigstrut}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{booktabs}
\usepackage{amsmath}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
	}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}
\usepackage{cite}

@@

  \begin{figure*}[t!]
    \centering
  \includegraphics[width=0.9\linewidth]{fig1}
  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
    diagram showing the ring gantry, and the radiation source}
  \label{fig1}

@@

\begin{figure}[htbp!]
  \centering
  \includegraphics[width=0.921\linewidth]{fig2}
  \caption{``Running start-stop'' mechanism as proposed in Ref. 
    \cite{Mackie1993}. (a)--(c) }
  \label{fig2}

@@

  For a more comprehensive history of this form of radiotherapy the readers 
  might want to refer to \cite{Mackie2006}.

  \section{Methods and Materials}
  \label{methods}
  \subsection{Construction}
  \label{construction}
  \subsubsection{A note on Serial Tomotherapy}
  \subsection{Radiation Characteristics}
  \label{radiation}
  \subsection{Comparisions between other conformal therapy techniques}
  \label{comparisions}
    \begin{table*}[htbp]
      \centering
      \caption{A comparision between standard and non-standard IMRT delivery 
      systems (Ref. \cite{Fenwick2006})}
      \small{
      \begin{tabulary}{\linewidth}{LLLLLLL}
        \toprule[0.04cm]

@@

      \label{tab:addlabel}%
    \end{table*}%
  \section{Clinical Results}
  \label{clinical}
  \subsection{Total Body Irradiation (TBI)}
  \subsection{Whole brain helical Tomotherapy}
  \subsection{Inoperable Lung Cancer}
  \subsection{Rectal Cancer}
  \section{Conclusion}
  \label{conclusions}
  \bibliography{Paper}{}
  \bibliographystyle{IEEEtran}

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran} %draftclsnofoot, 
\usepackage{graphicx}
\graphicspath{ {./_figures/} }
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\usepackage{bigstrut}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{booktabs}
\usepackage{amsmath}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
	}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}
\usepackage{cite}

@@

  \begin{figure*}[t!]
    \centering
  \includegraphics[width=0.89\linewidth]{fig1}
  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
    diagram showing the ring gantry, and the radiation source}
  \label{fig1}

@@

\begin{figure}[htbp!]
  \centering
  \includegraphics[width=0.9\linewidth]{fig2}
  \caption{``Running start-stop'' mechanism as proposed in Ref. 
    \cite{Mackie1993}. (a)--(c) }
  \label{fig2}

@@

  For a more comprehensive history the readers might want to refer to 
  \cite{Mackie2006}. The paper talks about the how this idea was 
  conceived and other technological advances led to its current state.

  \section{Methods and Materials}
  \label{methods}
  This section briefly discribes various aspects of helical tomography ranging 
  from it's construction and it's radiation characteristics to the differences 
  between it and other IMRT techniques.

  \subsection{Construction}
  \begin{figure}
    \centering
    \subfloat[\label{fig4a}][A simplified view of the Helical Tomotherapy 
    treatment head system in use today. The setup consists of a 6 MV linac to 
    produce an x-ray beam which is collimated down to a fan-beam using 2 
    moveable jaws (denoted as `y-jaws' in the image)]{
      \includegraphics[width=\linewidth]{fig4}}\\
    \subfloat[][]{
      \includegraphics[width=\linewidth]{fig5}}

  \end{figure}
  \label{construction}
  \subsubsection{A note on Serial Tomotherapy}
  \subsection{Radiation Characteristics}
  \label{radiation}
  \subsection{Comparisions between IMRT techniques}
  \label{comparisions}
    \begin{table*}[htbp!]
      \centering
      \caption{A comparision between standard and non-standard IMRT delivery 
      systems (Ref. \cite{Fenwick2006})}
      \small{
      \begin{tabulary}{\linewidth}{LLLLLLL}
        \toprule[0.04cm]

@@

      \label{tab:compare}%
    \end{table*}%
  Tomotherapy is different from other standard IMRT techiniques such as 
  conformal radiotherapy (CRT) techniques and non-standard IMRT techniques like 
  Cyber knife.   Standard CRT techniques generate highly conformal radiotherapy 
  using radiation fields generated in a few fixed-angle positions. These are 
  generated by linear accelerators (aka. LINAC) which are then modulated by 
  conventional leaf collimators operated in either dynamic mode or the standard 
  step-and-shoot mode. CyberKnife is a modern radiotherapy system developed by 
  Accuray, Inc., primarily for radiosurgery. It makes use of a highly precise 
  robotic arm to delivery the doses. The arm is computer driven to achieve very 
  high precision, it is mounted with a compact 6-MV LINAC whose orientation is 
  determined by 6 different mechanical subsystems. This robotic arm can be 
  moved with a much greater generality than most conventional sytsems. Table 
  \ref{tab:compare} highlights the key differences in various systems. For the 
  sake the completeness, the authors of Ref. \cite{Fenwick2006} have 
  dicotomized the conventional system into 2 types, with and without a 
  multileaf collimator, and the tomotherapy into serial and parallel 
  tomotherapy.
  \section{Clinical Results}
  \label{clinical}
  \subsection{Total Body Irradiation (TBI)}
  \subsection{Whole brain helical Tomotherapy}
  \subsection{Inoperable Lung Cancer}
  \subsection{Rectal Cancer}
  \section{Conclusion}
  \label{conclusions}
  \bibliography{Paper}{}
  \bibliographystyle{IEEEtran}
